On-the-fly Algorithms for GKAT Equivalences \thanks{Identify applicable funding agency here. If none, delete this.}

### 2025-01-19 main.tex
repo url
minor change to evaluation conclusion

\section{Implementation and Evaluation}
We implement our symbolic on-the-fly bisimulation algorithm~(\Cref{alg:symb-bisim}) in Rust along with derivative based~(\Cref{fig:derivatives-rules}) and Thompson's construction based~(\Cref{tab:symb-Thompson-construction}) algorithms for constructing symbolic GKAT coalgebras. The source code and benchmark suite is freely available in our repository TODO.

@@

We observe that all variants of DV and TC perform better than SymKAT in terms of time and memory usage. When comparing BDD to SAT, notice that BDD is marginally faster than SAT for smaller benchmarks, however, its time and memory usage degrades for larger ones. On the other hand, the performance of SAT is stable for all benchmarks. Furthermore, we have encountered BDD-degenerative expressions (the `degenerate' benchmark) which greatly reduce BDD performance but can be efficiently solved by SAT. We did not encounter any SAT-degenerative expressions where BDD performed significantly better than SAT.

>>>>

\section{Implementation and Evaluation}
We implement our symbolic on-the-fly bisimulation algorithm~(\Cref{alg:symb-bisim}) in Rust along with derivative based~(\Cref{fig:derivatives-rules}) and Thompson's construction based~(\Cref{tab:symb-Thompson-construction}) algorithms for constructing symbolic GKAT coalgebras. The source code and benchmark suite is freely available in our repository \url{https://anonymous.4open.science/r/rust-gkat-071E}.

@@

We observe that all variants of DV and TC perform better than SymKAT in terms of time and memory usage. When comparing BDD to SAT, notice that BDD is marginally faster than SAT for smaller benchmarks, however, its time and memory usage increases for larger ones. On the other hand, the performance of SAT is stable for all benchmarks. Furthermore, we have encountered degenerative expression pairs (the `degenerate' benchmark) which greatly reduce BDD performance but can be efficiently checked by SAT. We did not encounter any expression pairs where BDD performed significantly better than SAT.
